---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mspcompiler

<!-- badges: start -->
<!-- badges: end -->

The goal of mspcompiler is to offer ways to compile either EI or tandem mass
spectral libraries from various sources, such as NIST (if you have it installed),
MoNA, and GPNS, and organize them into a neat and up-to-date msp file that can 
be used in MS-DIAL. 

## Installation

Install \pkg{mspcompiler} by trying the following code.

``` r
# install.packages("devtools")
devtools::install_github("QizhiSu/mspcompiler", build_vignettes = TRUE)
```
If \pkg{ChemineR} and \pkg{ChemineOB} fail, please try:
```{r, eval=FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
        install.packages("BiocManager")

    BiocManager::install("ChemmineR")

    if (!requireNamespace("BiocManager", quietly = TRUE))
        install.packages("BiocManager")

    BiocManager::install("ChemmineOB")
```

Please read the vignettes to learn how to compile EI and tandem mass spectral 
libraries.
```{r, eval=FALSE}
browseVignettes("mspcompiler")
```
