---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mspcompiler

<!-- badges: start -->
<!-- badges: end -->

The goal of mspcompiler is to offer ways to compile either EI or tandem mass
spectral libraries from various sources, such as NIST (if you have it installed),
MoNA, and GPNS, and organize them into a neat and up-to-date msp file that can 
be used in MS-DIAL. 

## Installation

Install \pkg{mspcompiler} by trying the following code.

``` r
# install.packages("devtools")
devtools::install_github("QizhiSu/mspcompiler", build_vignettes = TRUE)
```
If \pkg{ChemineR} and \pkg{ChemineOB} fail, please try:
```{r, eval=FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
        install.packages("BiocManager")

    BiocManager::install("ChemmineR")

    if (!requireNamespace("BiocManager", quietly = TRUE))
        install.packages("BiocManager")

    BiocManager::install("ChemmineOB")
```

## Usage
Please read the vignettes to learn how to compile EI and tandem mass spectral 
libraries.
```{r, eval=FALSE}
browseVignettes("mspcompiler")
```


## Acknowledgement
Many thanks to Miao YU, the author of the enviGCMS R package, for his help to 
the read_lib function. I would also like to thank Dmitriy D. Matyushin for his 
hints to extract RI information from the NIST library. 
